---
title: "How to use context"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use context}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(context)
```

## Basic usage

Usage will be familiar to anyone that used Pythons `with-as` context manager.
For example, to iterate file line by line, run a function on a line, then do
something with the result:

```{r}

# Add numbers 1, 2, 3, 4, 5 to a file
set.seed(42)
temp_file <- tempfile()
writeLines(as.character(1:5), temp_file)
numbers <- c()

with(open(temp_file) %as% f, {
  while (read_line(f) %as% line) {
    numbers <- c(numbers, as.integer(line))
  }
})

cat("Sum of the numbers is: ", sum(numbers), "\n")
file.remove(temp_file) |> invisible()
```

In addition to the `with` context creation, `%as%` can be used to store the
value of the expression on its left side to the variable name on its right side.
When used in this manner, this type of assignment returns `FALSE` only when the
end of the is reached, that is when the length of the return value is zero. This
is useful when iterating through files in chunks; for example line by line or
block-by-block as is the case for example with `ShortRead::FastqStreamer()`.
